%!TEX root = ../cv.tex

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Other duties}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\vspace{1em}
\begin{flushleft}
\textbf{Supervising}
\end{flushleft}
\vspace{1em}

\descriptionstyle{
\begin{cvitems} % Description(s) bullet points
  \item {Co-supervisor for MSc project ``\textit{Substitution decomposition for permutation classes with infinitely many simple permutations}'' by Arnar Bjarni Arnarson (2019).}
  \item {Co-supervisor for MSc project ``\textit{Effective enumeration of permutation classes and their juxtapositions}'' by Unnar Freyr Erlendsson (2019).}
  \item {Aiding with the supervision of several MSc students including Ragnar Árdal, Bjarni Jens Kristinsson and Tomas Ken Magnússon on their projects related to permutation patterns.}
  \item {Supervisor for BSc project ``\textit{Identifying structure in Motzkin paths}'' by Björn Gunnarsson, Kolbeinn Erlingsson and Kristmundur Jónsson (2018).}
  \item {Supervisor for BSc project ``\textit{Identifying structures in set partitions}'' by James Robb and Sigurður Helgason (2018).}
  \item {Co-supervisor for BSc project ``\textit{Implementation of a planarity testing method using PQ-Trees}'' by Alex William Cregten and Hannes Kristján Hannesson (2017).}
  \item {Co-supervisor for BSc project ``\textit{PermPAL - Permutation Pattern Avoidance Library}'' by Arnar Bjarni Arnarson, Álfur Birkir Bjarnason, Sigurjón Freyr Viktorsson, and Unnar Freyr Erlendsson (2017).}
  \item {Co-supervisor for BSc project ``\textit{Generalized star polygons and star polygrams}'' by Eiður Sveinn Gunnarsson and Karl Þorláksson (2016).}
\end{cvitems}
}

%---------------------------------------------------------

\vspace{1em}
\begin{flushleft}
\textbf{Organisation of conferences:}
\end{flushleft}
\vspace{1em}

\descriptionstyle{
\begin{cvitems} % Description(s) bullet points
  \item {I was a member of the organising committee for Permutation Patterns 2017 held at Reykjavik University. (\url{https://pp2017.github.io})}
\end{cvitems}
}

% %---------------------------------------------------------
% \vspace{1em}
% \begin{flushleft}
% \textbf{Teaching assistant for:}
% \end{flushleft}
% \vspace{1em}
%
% {
% \begin{cvitems} % Description(s) bullet points
%   \item {}
% \end{cvitems}
% }

%---------------------------------------------------------

\vspace{1em}
\begin{flushleft}
\textbf{Review:}
\end{flushleft}
\vspace{1em}

\descriptionstyle{
\begin{cvitems} % Description(s) bullet points
  \item {European Journal of Combinatorics}
  \item {MathSciNet}
\end{cvitems}
}

\vspace{1em}
\begin{flushleft}
\textbf{Miscellaneous:}
\end{flushleft}
\vspace{1em}

\descriptionstyle{
\begin{cvitems} % Description(s) bullet points
  \item {Erd\H{o}s number is 3}
\end{cvitems}
}

\vspace{1em}
